Cryptographic assurance of secrecy and fairness in voting

### 2012-12-05 paper/paper.tex
Enable spell checking in Vim (modeline)
Describe "roles" from Preta, rewrite secrecy intro

A ``verifiable'' election is one in which the voters may rest assured that the body holding the
election (e.g., a government) reports final vote tallies that exactly reflect votes as they were
cast by the electorate.

@@

In many ways, ballot secrecy (often referred to as \term{receipt freeness}) is the most complicated security goal addressed by these systems.

Note that ballot secrecy is of vital importance for several reasons. In countries such as the United
States, it is a fundamental ``right'' that a voter is never required to reveal the candidate for
whom he/she voted. But in some third-world countries, the ability to determine one's chosen
candidate could determine that individual's life or death (e.g., a location in which a malevolent
dictator holds elections as a fa\c{c}ade). Therefore, it is crucial that one not be able to
determine how another voted.

This is also the most interesting goal, as secrecy complicates verifiability. It is only through use
of cryptography that systems such as those we study can provide verifiability without revealing how
individuals' votes were cast.

@@

Given a flawless implementation of Scantegrity as specified in research, it can certainly provide the
security it claims. However, we note that an amateur implementation of the protocol laid out by
Scantegrity's creators -- e.g., one that uses a non-perfect source of randomization -- could lead to
a very insecure system.

@@

% vim: set inde= colorcolumn=101 textwidth=100:

>>>>

An election involves an information exchange between many independent \term{voters} and a single
\term{election authority} organization.
In a verifiable election, each voter may verify that her own vote was counted correctly
by the election authority.
A voter, or any other third party \term{auditor}, may also verify the accuracy of the final tallies
reported by the election authority. \cite{preta}

@@

Countries such as the United States hold as a fundamental right that voting can be performed
in secret to reduce the possibility of voter coercion from any private entities.
In some developing states where corruption is prevalent, it may be desirable keep an
individual's vote hidden even from the election authority, again for the reason of
limiting coercibility. The latter goal is significantly more restrictive.

Ballot secrecy, often referred to as \term{receipt-freeness}, is perhaps the most complicated
security goal to address in a verifiable voting system.
Secrecy and verifiability are naturally at odds, and only through cryptography can we
reconcile these two requirements.

@@

Given a flawless implementation of Scantegrity as specified in research, it can certainly provide the
security it claims. However, we note that an amateur implementation of the protocol laid out by
Scantegrity's creators -- e.g., one that uses a imperfect source of randomization -- could lead to a
very insecure system.

@@

% vim: set inde= colorcolumn=101 textwidth=100 spell:
